---
title: "Weight of Fish"
author: "Melanie Vera"
date: "`r Sys.Date()`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
require(car)
require(leaps)
```

# Predicting Fish Weight
```{r}
fish <- read.csv(file = "Fish.csv")
```

```{r eval=TRUE}
 
fish <- fish %>%
mutate(across(where(is.character), as.factor))
levels(fish$Species)
Bream <- filter(fish, Species == "Bream")
Bream <- select(Bream, -Species) 
Parkki <- filter(fish, Species == "Parkki")
Parkki <- select(Parkki, -Species) 
Perch <- filter(fish, Species == "Perch")
Perch <- select(Perch, -Species) 
Pike <- filter(fish, Species == "Pike")
Pike <- select(Pike, -Species) 
Roach <- filter(fish, Species == "Roach")
Roach <- select(Roach, -Species) 
Smelt <- filter(fish, Species == "Smelt")
Smelt <- select(Smelt, -Species) 
Whitefish <- filter(fish, Species == "Whitefish")
Whitefish <- select(Whitefish, -Species) 
```

# For each of the three species of fish listed below, determine the best regression model and also the best 2 element regression model. Use the BestSubset Regression helper file.


## Perch

Find the best two predicters for weight of a Perch.

```{r}
Perchwtall=lm(Weight~.-Weight, data=Perch)
summary.lm(Perchwtall)
```

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Perch,
               nbest = 2,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```
  
##Which is best??  

```{r}
which.max(summary.out$adjr2)
```
```{r}
summary.out$which[3,]
```

```{r}
best.model <- lm(Weight~Height+Width,data=Perch)
summary(best.model)
```

```{r}
anova(best.model,Perchwtall)
```

###Best model

All variables are the best model.

###Best regressor model
Height and Width.

## Pike

```{r}
Pikewtall=lm(Weight~.-Weight, data=Pike)
summary.lm(Pikewtall)
```

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Pike,
               nbest = 2,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```
##Which is best??  

```{r}
which.max(summary.out$adjr2)
```
```{r}
summary.out$which[3,]
```

```{r}
best.model <- lm(Weight~Length1+Length3,data=Pike)
summary(best.model)
```

```{r}
anova(best.model,Pikewtall)
```

### Best Models

All variables are the best model.

### Best Two regressor model

Best 2 are Length1 and Length3

## Roach

```{r}
Roachwtall=lm(Weight~.-Weight, data=Roach)
summary.lm(Roachwtall)
```

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Roach,
               nbest = 2,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```
##Which is best??  

```{r}
which.max(summary.out$adjr2)
```
```{r}
summary.out$which[3,]
```
```{r}
best.model <- lm(Weight~Length3+Width,data=Roach)
summary(best.model)
```
```{r}
anova(best.model,Roachwtall)
```

### Best Models

All variables are the best model.

### Best Two regressor model

Best 2 are Length3 and Width

## Final Summary Statements
To conclude we used the helper file BestSubset_Regression.rmd. The best regresser model for Perch were Height and Width. The best regresser model for Pike were Length1 and Length3. the best regresser model for Roach were Length 3 and Width. in each of the Perch, Pike, and Roach, all variables were the best model.